A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-02-01 manuscript.Rmd
adept wording

We deem each concept necessary to archive longterm reproducibility.
However, which tools you use to implement these concepts are mere matter of taste and project requirements.
This tutorial will follow the recommendations of @Peikert2019 and utilizes Git for version control, RMarkdown for dynamic document creation, Make for dependency tracking, and Docker for software management.
Their interplay is shown in Figure \@ref(fig:schematic).
At several points, we suggest other viable alternatives.

```{r schematic, eval = TRUE, echo = FALSE, fig.cap="Schematic illustration of the interplay of the four components (in dashed boxes) central to the reproducible workflow: version control (Git), dependency management (Make), containerization (Docker), and dynamic document generation (R Markdown). Git tracks changes to the project over time. Make manages dependencies among the files. Docker provides a container in which the final report is built using dynamic document generation in R Markdown. Reproduced from @Peikert2019.  "}
# file gets downloaded in Makefile
knitr::include_graphics("images/nutshell.svg", auto_pdf = TRUE)
```

>>>>

We deem each concept necessary to archive longterm reproducibility.
However, which tools you use to implement these concepts is a matter of taste and project requirements.
This tutorial will follow the recommendations of @Peikert2019 and utilizes Git for version control, RMarkdown for dynamic document creation, Make for dependency tracking, and Docker for software management.
Their interplay is shown in Figure \@ref(fig:schematic).
At several points, we suggest other viable alternatives.

```{r schematic, eval = TRUE, echo = FALSE, fig.cap="Schematic illustration of the interplay of the four components (in dashed boxes) central to the reproducible workflow: version control (Git), dependency management (Make), software management (Docker), and dynamic document generation (R Markdown). Git tracks changes to the project over time. Make manages dependencies among the files. Docker provides a container in which the final report is built using dynamic document generation in R Markdown. Reproduced from @Peikert2019.  "}
# file gets downloaded in Makefile
knitr::include_graphics("images/nutshell.svg", auto_pdf = TRUE)
```
